Joint Likelihood Deconvolution of Astronomical Images in the Presence of Poisson Noise

### 2023-04-20 src/tex/ms.tex
[showyourwork] overleaf sync

    \begin{figure*}
        \script{comparison-scenarios.py}
        \begin{centering}
            \includegraphics[width=\linewidth]{figures/comparison-scenarios.pdf}
            \caption{
                Comparison of different deconvolution methods for different scenarios. The left column shows the raw simulated data and the second most column from the left the ground truth to comapare to. The simulation used a background level of "bg1 and a Gaussian PSF of \todo{x pixels}. The \textit{Pylira} method uses the \textit{Pylira} method with standard configuration. 
            }
            \label{fig:comparison-scenarios}
        \end{centering}
    \end{figure*}

    \subsubsection{Comparing Background Levels}
    Methods

@@

    \begin{equation}
        \label{eq:approx-sigma}
        \sigma = \frac{N_{\mathrm{Counts}} - N_{\mathrm{Pred}}} {\sqrt{N_{\mathrm{Pred}}}}
    \end{equation}

>>>>

    \begin{figure*}
        \script{comparison-scenarios.py}
        \begin{centering}
            \includegraphics[width=\linewidth]{figures/comparison-scenarios.pdf}
            \caption{
                Comparison of different deconvolution methods for different scenarios. The left column shows the raw simulated data and the second most column from the left the ground truth to comapare to. The simulation used a background level of "bg1 and a Gaussian PSF of \todo{x pixels}. The \textit{Pylira} method uses the \textit{Pylira} method with standard configuration.
                All results are available at \url{https://jolideco.github.io/jolideco-comparison}.
            }
            \label{fig:comparison-scenarios}
        \end{centering}
    \end{figure*}

    \subsubsection{Comparing Background Levels}
       \begin{figure*}
        \script{comparison-signal-noise.py}
        \begin{centering}
            \includegraphics[width=\linewidth]{figures/comparison-signal-noise.pdf}
            \caption{
                Comparison of Jolideco (GLEAM v0.1) for different signal to noise ratios.
                All results are available at \url{https://jolideco.github.io/jolideco-comparison}.
            }
            \label{fig:comparison-signal-noise}
        \end{centering}
    \end{figure*}

@@

    \begin{equation}
        \label{eq:approx-sigma}
        \sigma \approx \frac{\hat{N}_{\mathrm{Data}} - \hat{N}_{\mathrm{Pred}}} {\sqrt{\hat{N}_{\mathrm{Pred}}}}
    \end{equation}

    Where $\hat{N}$ is the weighted sum of counts from a Gaussian smoothing kernel.
    \todo{To account for the Poisson statistics it would be more precise to compute a "TS" map, but for an approximate estimation it should  be fine... }
